---
title: '20190509 Airbnb data'
author: "2018120094 류성균"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
```


## Airbnb data 개요
- 'Inside Airbnb' 프로젝트에서 제공(Murray Cox 주도)
- 주소 : http://insideairbnb.com/get-the-data.html
- 라이센스 : copyright : CC0 1.0 Universal (CC0 1.0) Public Domain Dedication - 비상업적 / 상업적 이용 가능(No copy right)
- 24개국 78개 도시 데이터 제공
j
```{r, echo=FALSE}
cities <- read.csv("../data/cities.csv", header=T, encoding = "UTF-8")
```

```{r, echo=FALSE}
cities %>% 
    group_by(continent) %>% 
    summarise(count_continent=n()) %>% 
    arrange(desc(count_continent)) %>% 
    kable()
```

```{r, echo=FALSE}
cities %>% 
    group_by(country, continent) %>% 
    summarise(count_city=n()) %>% 
    arrange(desc(count_city)) %>% 
    kable()
```

## 데이터셋 살펴보기
- Exploratory Data Analysis and Visualization of Airbnb Dataset (NYC, 2018-12; Ankit Peshin, Sarang Gupta, Ankita Agrawal, Colombia University)
- 링크 : https://github.com/Ankit-Peshin/airbnb

### 주요 주제 - NYC Airbnb 가격, 평점, 이용률, 리뷰
* How do prices of listings vary by location?
* How does the demand for Airbnb rentals fluctuate across the year and over years?
* Are the demand and prices of the rentals correlated?
* What are the different types of properties in NYC? Do they vary by neighborhood?
* What localities in NYC are rated highly by guests?
* What makes a host Super host?
* Do regular hosts and super hosts have different cancellation and booking policies?
* Are there any common themes that can be identified from the free-text section of the reviews? What aspects of the rental experience do people like and what aspects do they abhor?